Title: R Project
"

"
    "# Project 2 - ",
    "",
    "Team Members:",
    "    * Phyllis Summers",
    "    * Aparna Srikanti",
    "    * Helen Wu",
    "    ",
    "    ",
    "Purpose:",
    "",
    "    Using a Kaggle Dataset (https://www.kaggle.com/jrosenblum123/visualizations-and-predicting-student-test-scores) on ",
    "    Student Performance perform:",
    "    ",
    "    * Data Exploration",
    "    * Data Visualization leveraging R",
    "    * Identify regression between different points of data",
    "    * Identify if dependencies/correlation exist between different points of data",
    "    ",
    "    The Kaggle Dataset contains marks secured by the students in high school.  Students are from the United States.  ",
    "    There are 1000 sample records."
   ]
"


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load dataset and packages
```{r,warning=FALSE,message=FALSE}
### Load necessary packages
library(tidyverse)
library(dplyr)
library(psych)
library(relaimpo)
library(ggplot2)
library(ggthemes)
library(randomForest)
library(caTools)
library(miscTools)
library(rmarkdown)
library(pastecs)
library(Rmisc)
library(vioplot)
library(scatterplot3d)
library(caret)

library(RColorBrewer)
library(beeswarm)
```

```{r,warning=FALSE,message=FALSE}
# Read in dataset
students <- read.csv("StudentsPerformance.csv",h=T)

```

# Dataset Structure & summary
```{r,warning=FALSE,message=FALSE}
# Summary statistics
#str(students)
summary(students)
```

# Relationship of Test Scores with other key variables
The educational level of parents plays a significant role in a student's performance. 

# Key Drivers of Student performance By Shapley Value correlation using the `relaimpo` package.


```{r,warning=FALSE,message=FALSE eval=FALSE, include=FALSE}
# Regression
lm(math.score~.,students %>% dplyr::select(-writing.score,-reading.score)) %>% summary()
(calc.relimp(lm(math.score~.,students  %>% dplyr::select(-writing.score,-reading.score))))$lmg
(calc.relimp(lm(math.score~.,students  %>% dplyr::select(-writing.score,-reading.score))))$lmg %>% data.frame() %>% add_rownames(.,var = "variable") %>% ggplot(.,aes(variable,.,fill=variable)) + geom_bar(stat = "identity") + theme_fivethirtyeight() + theme(legend.title = element_blank())

lm(reading.score~.,students %>% dplyr::select(-writing.score,-math.score)) %>% summary()
(calc.relimp(lm(reading.score~.,students  %>% dplyr::select(-writing.score,-math.score))))$lmg %>% data.frame() %>% add_rownames(.,var = "variable") %>% ggplot(.,aes(variable,.,fill=variable)) + geom_bar(stat = "identity") + theme_fivethirtyeight() + theme(legend.title = element_blank())

lm(writing.score~.,students  %>% dplyr::select(-math.score,-reading.score)) %>% summary()
(calc.relimp(lm(writing.score~.,students  %>% dplyr::select(-math.score,-reading.score))))$lmg %>% data.frame() %>% add_rownames(.,var = "variable") %>% ggplot(.,aes(variable,.,fill=variable)) + geom_bar(stat = "identity") + theme_fivethirtyeight() + theme(legend.title = element_blank())
```
